Nail: A practical interface generator for data formats

### 2014-11-26 paper/login/eval.tex
Nail article

\section{Evaluation}
\label{s:eval}

@@

\subsection{Real-World Formats}
\label{s:eval-formats}

First, we'll demonstrate how Nail's features help process real-world protocols. We used Nail to implement grammars
for seven protocols with a range of challenging features.
Figure~\ref{fig:eval-protocols} summarizes our results.
We find that despite the challenging aspects of these protocols, Nail is
able to capture the protocols, by relying on its novel features: dependent
fields, streams, and transforms.  In contrast, state-of-the-art parser
generators would be unable to fully handle 5 out of the 7 data formats.

@@

\paragraph{DNS} In Section~\ref{s:design}, we introduced Nail's syntax with a grammar
for DNS packets, shown in Figure~\ref{fig:dns-full}.
The grammar corresponds almost directly to the diagrams in RFC 1035,
which defines DNS. Nail's dependent fields handle DNS's count fields, and
transformations represent label compression. Both of these features are awkward at best to handle
with existing tools.

@@

Nail avoids these issues by capturing these redundancies with dependent fields and decompressing
files transparently with transformations, and the programmer
is presented with a data structure containing the archive contents. Nail even allows parsing the
contents of an archive file -- allowing formats based on ZIP, such as Microsoft Office documents, to
be handled with one grammar.

>>>>

\section{Using Nail}
\label{s:eval}

@@

\subsection{Real-World Formats}
\label{s:eval-formats}
 We used Nail to implement grammars
for seven protocols with a range of challenging features.
Figure~\ref{fig:eval-protocols} summarizes our results.
Despite the challenging aspects of these protocols, Nail is
able to capture them by relying on its novel features: dependent
fields, streams, and transforms.  In contrast, state-of-the-art parser
generators would be unable to fully handle 5 out of the 7 data formats.

@@

\paragraph{DNS} Previously, we used a grammar for DNS packets shown in Figure~\ref{fig:dns-full} to
show how to write Nail grammars.
This example grammar corresponds almost directly to the diagrams in RFC 1035,
which defines DNS. Nail's dependent fields handle DNS's count fields, and
transformations represent label compression. Both of these features are awkward at best to handle
with existing tools.

@@

Nail captures these redundancies with dependent fields, eliminating the ambiguities. It also  decompresses
archive contents transparently with transformations, which allows parsing the
contents of an archive file -- allowing formats based on ZIP, such as Microsoft Office documents, to
be handled with one grammar.

### 2014-11-26 paper/login/intro.tex
Nail article

\begin{quote}
  I am ZIP, file of files.
  Parse me, ye mighty and drop a shell.

>>>>

\begin{quote}
Julian Bangert is a second year Ph.D. student working on computer security at MIT. When he is not
building parsers for complicated formats, he is interested is building exploit mitigation
techniques, side-channel resistant cryptography and finding turing-complete weird machines in
unexpected places, such as your processors virtual memory system.

Nickolai Zeldovich is an Associate Professor at MIT's department of Electrical Engineering and Computer Science, and a member of the Computer Science and Artificial Intelligence Laboratory. His research interests are in building practical secure systems, from operating systems and hardware to programming languages and security analysis tools. He received his PhD from Stanford University in 2008, where he developed HiStar, an operating system designed to minimize the amount of trusted code by controlling information flow. In 2005, he co-founded MokaFive, a company focused on improving desktop management and mobility using x86 virtualization. Prof. Zeldovich received a Sloan fellowship (2010), an NSF CAREER award (2011), the MIT EECS Spira teaching award (2013), and the MIT Edgerton faculty achievement award (2014).
\end{quote}
\begin{quote}
  I am ZIP, file of files.
  Parse me, ye mighty and drop a shell.
